\documentclass[a4paper,12pt,leqno]{report}
\title{introduction}
\usepackage[options]{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage[backgroundcolor=red!40,outlinewidth = 3cm]{mdframed}
\usepackage[T1]{fontenc}
\usepackage{tgbonum}

\begin{document}

\maketitle	
	You would put your text where the dots are. The reason for marking off the beginning of your text is that  allows you to insert extra setup specifications before it (where the blank line is in the example above: we'll be using this soon). The reason for marking off the end of your text is to provide a place for to be programmed to do extra stuff automatically at the end of the document, like making an index.	
\textbf{You would put your text where the dots are. The reason for marking off the beginning of your text is that  allows you to insert extra setup specifications before it (where the blank line is in the example above: we'll be using this }soon). The reason for marking off the end of your text is to provide a place for to be programmed to do extra stuff automatically at the end of the document, like making an index.
\section*{A-abstraction}
\begin{mdframed}
You would put your text where the dots are. The reason for marking off the beginning of your text is that allows you to insert extra setup specifications before it (where the blank line is in the example above: we'll be using this soon). The reason for marking off the end of your text is to \linebreak to do extra stuff automatically at the end of the document, \linebreak like making an index.
\end{mdframed}
\textcolor{yellow}{
\section*{B-Mechanical Design}}
You would put your text where the dots are. The reason for marking off the beginning of your text is that  allows you to insert extra setup specifications before it (where the blank line is in the example above: we'll be using this soon). The reason for marking off the end of your text is to provide a place for to be programmed to do extra stuff automatically
 at the end of the document, like making an index.
\textcolor{red}{
\subsection*{1-ROV Design}}
You would put your text where the dots are. The reason for marking off the beginning of your text is that  allows you to insert extra setup specifications before it (where the blank line is in the example above: we'll be using this soon). The reason for marking off the end of your text is to provide a place for to be programmed to do extra stuff automatically at the end of the document, like making an index see equation \ref{equation 1}
\begin{equation}
	x=\frac{3}{8}
\end{equation}

\begin{equation}\label{equation 1}
x=\frac{3}{7}
\end{equation}

\end{document}
	